Trending assessment for nowcasts, measurements, and forecasts

### 2024-02-20 sections/02-notation.tex
Update on Overleaf.

Measurement aims to obtain accurate and reliable data about the current state of a system. Often a certain parameter or variable is measured at regular intervals over a certain period of time.
An important question is how to compare one method of measurement of a variable with another.
For this purpose, measured values can be recorded with the two measurement methods to be compared. One can be the gold standard, we note the measured values from the gold standard method with $(y_t)^T_{t=0}$) for the same variable in the same period of time. 
The measured values for a measurement method are then available in a time series form, can be noted with $(x_t)^T_{t=0}$. 
To detect the systematic difference between the two methods, a paired t-test can be performed on the pairwise difference of the two series of measurements to test the null hypothesis that the true mean difference is zero (\cite{watson2010method}).
In addition, various indices such as the interclass correlation coefficient or Lin's concordance correlation, which were originally introduced as a modification of the Pearson correlation, have been proposed in practice to check the reproducibility of the measurement or to compare different measurement methods (\cite{lawrence1989concordance,koo2016guideline,}). 
Furthermore, graphical tools were developed, such as the Bland-Altman diagram, which visualizes the differences between the methods in relation to their mean value (\cite{bland1986statistical}).

>>>>

Measurement aims to obtain accurate and reliable data about the current state of a system. Often a certain parameter or variable is measured at regular intervals over a certain period of time.
An important question is how to compare one method of measurement of a variable with another.
For this purpose, measured values can be recorded with the two measurement methods to be compared. One can be the gold standard, we note the measured values from the gold standard method with $(y_t)^T_{t=0}$ for the same variable in the same period of time. 
The measured values for a measurement method are then available in a time series form, can be noted with $(x_t)^T_{t=0}$. 
To detect the systematic difference between the two methods, a paired t-test can be performed on the pairwise difference of the two series of measurements to test the null hypothesis that the true mean difference is zero (\cite{watson2010method}).
In addition, various indices such as the interclass correlation coefficient or Lin's concordance correlation, which were originally introduced as a modification of the Pearson correlation, have been proposed in practice to check the reproducibility of the measurement or to compare different measurement methods (\cite{lawrence1989concordance,koo2016guideline,}). 
Furthermore, graphical tools were developed, such as the Bland-Altman diagram, which visualizes the differences between the methods in relation to their mean value (\cite{bland1986statistical}).
